---
title: "Swirl"
author: "Winston Wong"
date: "10/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
"11/1/2021: Finished Sequences of Numbers module and 2 problems from Basic R Exercises"
"11/2/2021: Finished `Vectors` module and Missing values module"
"11/3/2021: Finished `Subsetting Vectors` and 2 problems from Basic R Exercises"
"11/4/2021: Finished Matrices and Data Frames module, and Logic module, and 1 problem from Basic R Exercises"
"11/5/2021: Attempted to understand the sieve of Eursthanese problem, and worked on Functions module in Swirl"
"11/6/2021: Finished Functions module"
"11/8/2021: Worked on one problem from Basic R Exercises"
"11/9/2021: Finished lapply and sapply module"
"11/11/2021: Finished vapply and tapply module"
```

```{r}
"Write a R program to extract first 10 english letter in lower case and last 10 letters in upper case and extract letters between 22nd to 24th letters in upper case."

alphabet <- c("a","b","c","d","e","f","g","h","i","j","k","l","m","n","o",
              "p","q","r","s","t","u","v","w","x","y","z")

alphabet[1] <- "a"

for (i in 1:26){
  if (i == 23){
    print("23rd letter in uppercase")
    print(toupper(alphabet[23]))
  }
  else if (i == 17:26){
    print("Last 10 letters in uppercase")
    print(toupper(alphabet[17:26]))
  }
  else if (i == 1:10){
    print("First 10 letters in uppercase")
    print(tolower(alphabet[1:10]))
  }
}


```


```{r}
"Write a R program to get all prime numbers up to a given number (based on the sieve of Eratosthenes)."

prime_numbers <- function(n) {
if (n >= 2) {
 x = seq(2, n)                                  #Generate sequence from 2:n
 prime_nums = c()
 for (i in seq(2, n)) {                         #For any number inside 2:n...
 if (any(x == i)) {                             #If any number inside 2:n equals i, then...
 prime_nums = c(prime_nums, i)                  #Combine existing prime_nums with i, and...
 x = c(x[(x %% i) != 0], i)                     
 }
 }
 return(prime_nums)
 }
 else 
 {
 stop("Input number should be at least 2.")
 }
 } 
```

```{r}
"Write a R program to create three vectors a,b,c with 3 integers. Combine the three vectors to become a 3×3 matrix where each column represents a vector. Print the content of the matrix."

a <- c(1,2,3)
b <- c(4,5,6)
c <- c(7,8,9)

cvec <- c(a,b,c)
cvec_matrix <- matrix(cvec, nrow =3)
colnames(cvec_matrix) <- c("a","b","c")
```

You can exit swirl and return to the R prompt (>) at any time by pressing the Esc
| key. If you are already at the prompt, type bye() to exit and save your progress.
| When you exit properly, you'll see a short message letting you know you've done so.

| When you are at the R prompt (>):
| -- Typing skip() allows you to skip the current question.
| -- Typing play() lets you experiment with R on your own; swirl will ignore what you
| do...
| -- UNTIL you type nxt() which will regain swirl's attention.
| -- Typing bye() causes swirl to exit. Your progress will be saved.
| -- Typing main() returns you to swirl's main menu.
| -- Typing info() displays these options again.


